How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-22 tse-paper/paper.tex
First feedback and review integrated

\author{Carolin~Brandt,%~\IEEEmembership{Member,~IEEE,}
        Moritz~Beller,%~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
% \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
% GA, 30332.\protect\\
% % note need leading \protect in front of \\ to get a newline within \thanks as
% % \\ is fragile and will error, could use \hfil\break instead.
% E-mail: see http://www.michaelshell.org/contact.html
% \IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
\thanks{Manuscript received May 1, 2020; revised August 26, 2015.}}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Computer Society, IEEE, IEEEtran, Journal, Continuous Integration, 
Build Log Analysis, Chunk Retrieval.
\end{IEEEkeywords}}

>>>>

\author{Carolin~Brandt,%~\IEEEmembership{Member,~IEEE,}
        Moritz~Beller%~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
% \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
% GA, 30332.\protect\\
% % note need leading \protect in front of \\ to get a newline within \thanks as
% % \\ is fragile and will error, could use \hfil\break instead.
% E-mail: see http://www.michaelshell.org/contact.html
% \IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
\thanks{Manuscript received May 1, 2020; revised August 26, 2015.}}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Build Log Analysis, Chunk Retrieval, Continuous Integration
\end{IEEEkeywords}}
